The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-09-14 paper/mnras/paper.tex
update

Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  \jillianremark{  For Type II supernovae, iron and oxygen are produced according to the analytic fits used in \citet{Raiteri96} using the yields from \citet{Woosley95}:

@@

We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  }

@@

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.   Once created,  metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion parameter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.  
{\bf Combined with infall, this procedure produces a range of metallicities within each galaxy.  
}

@@

\subsection{Mass-metallicity-SFR relation}

{\bf

Simulations and observations suggest that galaxies only  exist with a relatively narrow range of possible masses,
metallicities, and star formation rates; see, e.g., \citet{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H}.   For example,  
\cite{2016MNRAS.tmp.1187H} suggest a correlation beteween mass, metallicity, and star formation rate
\begin{eqnarray}
12+\log [O/H] = -0.14 log (SFR) + 0.37 log (M_*) + 4.82
\end{eqnarray}
In particular, taking this expression at face value, the star formation rate and metallicity are anticorrelated: a high
star formation rate can occur only at low metallicity.  
Figure XXXX shows the trajectories of our fiducial simulations' median $Z$ and star formation rate, using this
diagnostic.  ARE THEY REASONABLE?

}

@@

To explore plausible binary detection scenarios, we adopt a parametrized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \cite[][(hereafter \abbrvPSgrb{})]{PSgrbs-popsyn} and  \citet[][(hereafter \abbrvPSellipticals{})]{PSellipticals};  similar approaches have been used by
\cite{2016arXiv160508783L} and others.
{\bf 
Since prior population synthesis investigations  extend relatively smoothly to very metallicity, we do not introduce a
distinct, special group of low-metallicity Population III stars.
}

@@

{\bf In our investigation, we have neglected the impact of population III stars.
Previous studies suggest the first generation of stars may contribute a small but nonzero fraction of detectable events,
potentially with distinctively high black hole masses
\cite{2016MNRAS.460L..74H,2016PhRvL.117f1101S,2014MNRAS.442.2963K}.  
% http://adsabs.harvard.edu/abs/2004ApJ...612..597W
}

>>>>

Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{Raiteri96}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.    For Type II supernovae, iron and oxygen are produced according to the analytic fits used in \citet{Raiteri96} using the yields from \citet{Woosley95}:

@@

@@

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.   Once created,  metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion parameter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.  
Combined with infall, this procedure produces a range of metallicities within each galaxy.

We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  We cannot thus discuss Population III contributions to the gravitational wave background; however, studies by  \citet{Hartwig16}  and \citet{Dvorkin16} suggest that this contribution is fairly negligible.  We have shown that our scheme for metal production and distribution produces galaxies which match the mass-metallicity relation at $z \sim 3$ \citep{Brooks07} as well as in the local universe \citep{Christensen16}.  At higher redshifts, there is a very large spread in the metal distributions of damped Lyman alpha systems \citep{Dvorkin15}; manifestly, other features in the galaxy evolutionary history play a role in its present day metallicity.  Recently \citet{Hunt16a,Hunt16b} has demonstrated a relationship between of the mass, metallicity, and star formation rate, which demonstrates an evolutionary relationship between these quantities.  As we will discuss in future work, we have verified that our evolutionary prescriptions are also qualitatively consistent with this relation.

@@

%\subsection{Mass-metallicity-SFR relation}
%
%{\bf
%
%Simulations and observations suggest that galaxies only  exist with a relatively narrow range of possible masses,
%metallicities, and star formation rates; see, e.g., \citet{2010MNRAS.408.2115M,2016MNRAS.tmp.1187H}.   For example,  
%\cite{2016MNRAS.tmp.1187H} suggest a correlation beteween mass, metallicity, and star formation rate
%\begin{eqnarray}
%12+\log [O/H] = -0.14 log (SFR) + 0.37 log (M_*) + 4.82
%\end{eqnarray}
%In particular, taking this expression at face value, the star formation rate and metallicity are anticorrelated: a high
%star formation rate can occur only at low metallicity.  
%Figure XXXX shows the trajectories of our fiducial simulations' median $Z$ and star formation rate, using this
%diagnostic.  ARE THEY REASONABLE?
%
%
%}

@@

To explore plausible binary detection scenarios, we adopt a parametrized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \cite[][(hereafter \abbrvPSgrb{})]{PSgrbs-popsyn} and  \citet[][(hereafter \abbrvPSellipticals{})]{PSellipticals};  similar approaches have been used by
\cite{2016arXiv160508783L} and others.  Since prior population synthesis investigations  extend relatively smoothly to very metallicity, we do not introduce a
distinct, special group of low-metallicity Population III stars.

@@

In our investigation, we have neglected the impact of population III stars.
Previous studies suggest the first generation of stars may contribute a small but nonzero fraction of detectable events,
potentially with distinctively high black hole masses
\citep{2016MNRAS.460L..74H,2016PhRvL.117f1101S,2014MNRAS.442.2963K}.  
% http://adsabs.harvard.edu/abs/2004ApJ...612..597W
